---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


# Quebec Covid19 data 

## UPDATE April 8, 2020

The data is now in `.csv` format directly, so no need to parse JSON.


## March 31, 2020

I parsed the `JSON` behind [the INSPQ highcharts](https://www.inspq.qc.ca/covid-19/donnees) using `R` and reproduced the graphs with `ggplot2`. 

* The cleaned data used to generate these graphs can be found in the [`data`](https://github.com/sahirbhatnagar/covid19/tree/master/data) folder.  
* The code used to scrape the data, clean it and plot it can be found at http://sahirbhatnagar.com/covid19/.  
* The `R` script can be found in the [`bin`](https://github.com/sahirbhatnagar/covid19/tree/master/bin) folder

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.width = 9, fig.height = 8, collapse = TRUE)
pacman::p_load(here)
knitr::read_chunk(here::here("bin/scrapper.R"))
```


# Load Required Packages {-}

```{r load-packages}
```




# 1- Évolution quotidienne des nouveaux cas et du nombre cumulatif de cas liés à la COVID-19 au Québec {-}

```{r clean-data-1}
```

```{r graph-1}
```



# 2 - Évolution quotidienne des décès et du nombre cumulatif de décès liés à la COVID-19 au Québec {-}

```{r clean-data-2}
```

```{r graph-2}
```



# 3 - Évolution quotidienne du nombre d'hospitalisations liées à la COVID-19 au Québec {-}

```{r clean-data-3}
```

```{r graph-3}
```



# 4 - Évolution quotidienne des nombres cumulatifs de cas confirmés et de personnes avec des analyses négative {-}

```{r clean-data-4}
```

```{r graph-4}
```



# 7 - Cas confirmés selon le groupe d'âge (répartition et taux pour 100 000) {-}


```{r clean-data-7}
```

```{r graph-7}
```




# Code of Conduct

Please note that the 'covid19' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
